---
title: "Biden Polling"
format: html
execute: 
  echo: false
---

Voting preferences vary across demographic groups and are shaped by complex social factors. Using data from a March 2024 survey of 1,559 respondents, we examine what proportion of votes will be cast for Joe Biden in the 2024 U.S. presidential election.
However, our estimate may be biased because the survey respondents might not be fully representative of the actual voting population in November.
We model voter support for Joe Biden, measured as a binary outcome (support or not), as a logistic function of a single intercept term with no covariates.

```{r setup}
#| message: false
library(tidymodels)
library (tidyverse)
library(broom)

poll_data <- tibble(biden = as.factor(c(rep("Yes", 655), 
                                        rep("No", 904)))) |> 
                slice_sample(prop = 1)

```

$$
\log\left(\frac{\hat{p}}{1 - \hat{p}}\right) = -0.32
$$

$$
\hat{p} = \frac{1}{1 + e^{-(-0.32)}} \approx 0.42
$$

```{r}
#| cache: true


fit_biden <- logistic_reg() |> 
  fit(biden ~ 1, data = poll_data)

```


```{r}
#| cache: true

library(broom)
library(gt)

# Tidy model output and create formatted table
tidy(fit_biden, conf.int = TRUE) |>
  select(term, estimate, conf.low, conf.high) |>
  mutate(
    estimate = round(estimate, 3),
    conf.low = round(conf.low, 3),
    conf.high = round(conf.high, 3)
  ) |>
  gt() |>
  cols_label(
    term = "Term",
    estimate = "Estimate",
    conf.low = "95% CI (Lower)",
    conf.high = "95% CI (Upper)"
  ) |>
  tab_header(
    title = "Estimated Support for Joe Biden (Intercept-Only Model)"
  ) |>
  tab_source_note(
    source_note = "Source: YouGov Poll, March 10–12, 2024"
  ) |>
  tab_caption(
    caption = "This logistic regression model estimates the log-odds of support for Joe Biden based on survey responses."
  )
```
